The Error Estimate of Force Calculation in the Inhomogeneous Molecular Systems

### 2011-10-19 shortRange.inhomo/writeDown/main.tex
add slides

We studied the liquid-vapor equilibrium and the collision of nanoscale
Lennard-Jones cluster to demonstrate the validity of the proposed
methods.  All simulation results were compared with the uniform
cut-off simulations, in which very large cut-off radii were used to
achieve real convergence.  With the same maximum RMS force error,
the precision of physical properties of the adaptive cut-off method
were the same as the uniform cut-off method. From the efficiency
point of view, the advantage of the adaptive cut-off method depends on the
system: if the large bulk regions are connected by high density
gradient interfaces, the adaptive cut-off method will save a large amount of
computational cost.  In the liquid-vapor equilibrium simulation, the
force correction method improved the force accuracy by one order of
magnitude without large extra computational expense. The physical
properties converged at cut-off $r_c^\ast = 3.5$, whereas the uniform
cut-off method converged at much larger cut-off radii ($r_c^\ast = 6.0$
for surface tension and $r_c^\ast = 10.0$ for equilibrium
densities). With nearly the same RMS force error, precision of
equilibrium densities of the force correction simulation were much
better than the uniform cut-off simulation.  Since the homogeneity
error dominated the force correction and the inhomogeneity error
dominated the uniform cut-off simulation, we conclude the homogeneity
error and the inhomogeneity error play different roles on the precision
of equilibrium liquid-vapor densities.  In the collision cluster case,
the force correction methods produced high-precision trajectory at a
very small cut-off radius $r_c^\ast=2.5$, with which the uniform
cut-off method was qualitatively wrong. However, due to the
inconsistency of the cluster movement and the correction force
computation, small deviations of angular velocity and momentum were
observed.

>>>>

We studied the liquid-vapor equilibrium and the collision of nanoscale
Lennard-Jones cluster to demonstrate the validity of the proposed
methods.  All simulation results were compared with the uniform
cut-off simulations, in which very large cut-off radii were used to
achieve real convergence.  With the same maximum RMS force error,
the precision of physical properties of the adaptive cut-off method
were the same as the uniform cut-off method. From the efficiency
point of view,
the adaptive cut-off simulation saved 34\% -- 50\% computational cost
in liquid-vapor simulation and 18\% in the cluster collision simulation.
The advantage of the adaptive cut-off method depends on the
system: if the large bulk regions are connected by high density
gradient interfaces, the adaptive cut-off method will save a large amount of
computational cost.

In the liquid-vapor equilibrium simulation, the
force correction method improved the force accuracy by one order of
magnitude without large extra computational expense. The physical
properties converged at cut-off $r_c^\ast = 3.5$, whereas the uniform
cut-off method converged at much larger cut-off radii ($r_c^\ast = 6.0$
for surface tension and $r_c^\ast = 10.0$ for equilibrium
densities). With nearly the same RMS force error, precision of
equilibrium densities of the force correction simulation were much
better than the uniform cut-off simulation.  Since the homogeneity
error dominated the force correction and the inhomogeneity error
dominated the uniform cut-off simulation, we conclude the homogeneity
error and the inhomogeneity error play different roles on the precision
of equilibrium liquid-vapor densities.  In the collision cluster case,
the force correction methods produced high-precision trajectory at a
very small cut-off radius $r_c^\ast=2.5$, with which the uniform
cut-off method was qualitatively wrong. However, due to the
inconsistency of the cluster movement and the correction force
computation, small deviations of angular velocity and momentum were
observed.

\section*{Acknowledgements}
The authors gratefully thank Luigi Delle Site for for useful comments
on the manuscript. The work of P.Z. is supported by grants from
National Natural Science Foundation of China (20490222).
